Paper 2: Vitamin D

### 2017-11-27 doc/vitaminD.Rmd
adjusted figures to match seminar slides

# Box plot of uVDBP in different albuminuria categories
vitd %>% 
  box_plot("vitdStatus", "log(udbpCr)", 
            "Vitamin D Status",
            "log uVDBP:cr (μg/mmol)")

@@

dsBase %>% 
  scatter_plot("log(VitaminD)", "log(udbpCr)", 
               "log serum 25(OH)D",
               "log UDBP:Creatinine")

@@

dsBase %>% 
  dplyr::mutate(lVitD = log(VitaminD)) %>% 
  prep_mason_data() %>% 
  mason_glm(y = "logudbpCr",
            x = "lVitD",
            covars = c("ageBase", "Sex", "Ethnicity", "BMI", "MET", "Season", "dmStatus")
            ) %>% 
  gee_results_table() %>% 
  pander::pander()

@@

gee_vitd_baseline <- ds %>% 
  prep_mason_data_vitd() %>% 
  mason_geeplot(y = "lVitD",
            x = "udbpCrBase",
            covars = c("MonthsFromBaseline", "ageBase", "Sex", 
                       "Ethnicity", "MET", "BMI", "dmStatus", "Season"),
            intvar = "Season") %>% 
  mason::polish_renaming(rename_gee_vitd)

@@

gee_vitd <- ds %>% 
  prep_mason_data_vitd() %>% 
  mason_geeplot(y = "lVitD",
            x = "udbpCr",
            covars = c("MonthsFromBaseline", "ageBase", "Sex", "Ethnicity", "MET", "BMI", "dmStatus", "Season"),
            intvar = "Season") %>% 
  mason::polish_renaming(rename_gee_vitd)

>>>>

# Box plot of uVDBP in different albuminuria categories
vitd %>% 
  box_plot_slides("vitdStatus", "log(udbpCr)", 
            "Vitamin D Status",
            "log uVDBP:cr (μg/mmol)")

@@

dsBase %>% 
  scatter_plot_slides("log(VitaminD)", "log(udbpCr)", 
               "log serum 25(OH)D",
               "log uVDBP:cr (μg/mmol)")

@@

dsBase %>% 
  dplyr::mutate(lVitD = log(VitaminD)) %>% 
  prep_mason_data() %>% 
  mason_glm(y = "logudbpCr",
            x = "lVitD",
            covars = c("ageBase", "Sex", "Ethnicity", "MET", "Season", "dmStatus")
            ) %>% 
  gee_results_table() %>% 
  pander::pander()

@@

gee_vitd_baseline <- ds %>% 
  prep_mason_data_vitd() %>% 
  mason_geeplot(y = "lVitD",
            x = "udbpCrBase",
            covars = c("MonthsFromBaseline", "ageBase", "Sex", 
                       "Ethnicity", "MET", "dmStatus", "Season"),
            intvar = "Season") %>% 
  mason::polish_renaming(rename_gee_vitd)

@@

gee_vitd <- ds %>% 
  prep_mason_data_vitd() %>% 
  mason_geeplot(y = "lVitD",
            x = "udbpCr",
            covars = c("MonthsFromBaseline", "ageBase", "Sex", "Ethnicity", "MET", "dmStatus", "Season"),
            intvar = "Season") %>% 
  mason::polish_renaming(rename_gee_vitd)
